\documentclass[11pt] {article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{array}
\usepackage{enumitem}
\newcolumntype{C}{>$c<$}
\newcolumntype{L}{>$l<$}

\begin{document}
\begin{flushleft}
Rowan Lochrin\\
MATH3066\\
Homework 1\\
26/4/17\
\end{flushleft}
\begin{enumerate}
\item 
\begin{enumerate}
\item The integer 57 is Prime (Well defined False)
\item The integer 57 is a Grothendieck prime. (Well defined True)
\item London is in England. (Undefined)
\item This sentence is False (Undefined)
\end{enumerate}
\item
\begin{enumerate}
\item If the sun is shining we are headed to the surf. \newline
\textit{Converse:} We are headed to the surf so the sun is shining. \newline
\textit{Contrapositive:} We are not headed to the surf so the sun is not shining.
\item If I have listened attentively I will do well in the exam. \newline
\textit{Converse:} If I did well on the exam I have listened closely. \newline
\textit{Contrapositive:} If I did not do well on the exam I have not listened closely.
\item It is necessary to have a valid passport to log on to my computer. \newline
\textit{Converse:} If I logged on to my computer I had a valid password. \newline
\textit{Contrapositive:} If I didn't have a valid passport I have not logged in to my computer. 
\item Only if my attendance is recorded will I be bothered coming to tutorials.\newline
\textit{Converse:} If I am coming to tutorial my attendance is being recorded \newline
\textit{Contrapositive:} If I am not coming into tutorials my attendance is not being recorded.
\end{enumerate}
\item
\begin{enumerate}
\item
\[
\begin{array}{C|C|C|C|C}
$P$ & $Q$ & $P \Rightarrow Q$ & $[P \land (P\Rightarrow Q)] $ &$ [P \land (P\Rightarrow Q)] \Rightarrow Q$\\ \hline
T & T & T & T &  T\\
T & F & F & F & T\\
F & T & T & F & T\\
F & F & T & F & T\\

\end{array}
\]
\item
\[
\begin{array}{C|C|C|C|C|C|C}
$P$ & $Q$ & $\sim P$ & $\sim Q $ &$ P \Rightarrow Q $ & $ \sim  Q \land (P\Rightarrow Q) $& $ [\sim Q \land (P\Rightarrow Q)] \Rightarrow \sim P$\\ \hline
T & T & F & F & T & F & T\\
T & F & F & T & F & F  & T\\
F & T & T & F & T & T & T\\
F & F & T & T & T & T & T\\

\end{array}
\]
\end{enumerate}
\item
\begin{enumerate}
\item
\[
\begin{array}{C|C|C|C}
$P$ & $Q$ & $R$ & $(P \lor Q) \lor R $\\ \hline
T & T & T & T\\
T & T & F & T\\
T & F & T & T\\
T & F & F & T\\
F & T & T & T\\
F & T & F & T\\
F & F & T & T\\
F & F & F & F\\
\end{array}
\]
\item
\[
\begin{array}{C|C|C|C}
$P$ & $Q$ & $R$ & $(P \land Q) \lor R $\\ \hline
T & T & T & T\\
T & T & F & T\\
T & F & T & T\\
T & F & F & F\\
F & T & T & T\\
F & T & F & F\\
F & F & T & T\\
F & F & F & F\\

\end{array}
\]
\end{enumerate}
\end{enumerate}
 \end{document}