\documentclass[11pt]{article}

\usepackage{scrextend}
\usepackage[a4paper, margin = 1in,footskip =0.25in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{graphicx}

\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}

\graphicspath{ {images/} }

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}


\begin{document}
\begin{flushleft}
	Rowan Lochrin \\
	MATH415B - Klaus Lux \\
	1/29/18 \\
	Homework 5
\end{flushleft}
\begin{description}
	\item[12] Determine which of the polynomials are irreducible over $Q$.
		\begin{enumerate}
			\item $x^5 + 9x^4 + x^2 + 1$
				By Eisenstein's criterion $p=3$
				$$3 \nmid, 3\mid 9, 3 \mid 2, 3\mid 6, 3^2\nmid 6$$
			\item $x^4 + x + 1$
			Suppose
				$$x^4 + x + 1  = 0 $$
				by the mod $p$ irreduciblity test we seek to
				show that it is irreducible mod $2$.
				Note that because $1$ is a term it can have no
				linear factors so
				$$x^4+x+1 = (x^2 + ax + 1)(x^2 + bx +1) $$ 
				and we can no pair of values for $a,b \in {0,1}$
				make this true.
			\item $x^4 + 3x^2 + 3$
				By Eisenstein's criterion $p=3$
				$$ 3 \nmid 1, 3\mid 3, 3 \mid 3, 3^2\nmid 3 $$
			\item $x^5 + 5x^2 + 1 $
				by the mod $p$ irreduciblity test we seek to
				show that it is irreducible mod $5$.
				$$x^5 + 1 \text{ mod } 5$$
				We can see that it has no linear factors
			\item $(5/2)x^5 + (9/2)x^4 + 15x^3 + (3/7)x^2 + 6x + 3/14$
			\begin{align*}
				& 14(x^5 + (9/2)x^4 + 15x^3 + (3/7)x^2 + 6x + (3/14)) \\
				 & =  14x^5 + 63x^4 + 210x^3 + 6x^2 + 84x +3 
			\end{align*}
				By Eisenstein's criterion $p=3$
				$$ 3 \nmid 14, 3\mid 63, 3 \mid 210, 3 \nmid 6,
				3 \mid 84, 3\mid 3, 3^2 \mid 3 $$
				So because our original polynomial is a unit
				times a reducible polynomial it also must be
				reducible.
		\end{enumerate}
	\item[20] Prove that, for every positive integer $n$, there are
		infinitely many polynomials of degree $n$ in $Z[x]$ that are
		irreducible over $q$.\\
		\begin{proof}
		For any prime $p$ consider the polynomial
			$$ (p+1)x^n + px^{n-1} + ... + p $$
		We can see that
			$$ p \nmid (p+1), p\mid p, p^2 \mid p$$
		so Eisenstein's criterion it is irreducible in $Q$ and therefore
		must be irreducible of $Z$. Because there are infinitely many
			primes there must be infinitely many such polynomials.
		\end{proof}
	\item[24] Given that $\pi$ is not the zero of a nonzero polynomials with
		rational coefficients, prove that $\pi^2$ cannot be written in
		the form $a\pi+b$ where $a$ and $b$ are rational.\\
		\begin{proof}
		 Because $\pi$ is a nonzero polynomial, Deg $\pi \geq 1$ so deg
			$\pi^2 > 2 \text{ deg }$ deg $a\pi+b = \deg \pi$.
		\end{proof}
	\item[27] Let 
		$$ f(x) = a_nx^n + a_{n-1}x^{n-1} + ... + a_0 \in Z[x]$$
		and $a_n \neq 0$. Prove that if $r$ and $s$ are relatively prime
		$f(r/s) = 0$, then $r\mid s$ and $s \min a_n$.\\
		\begin{proof}
			$$ f(r/s) = a_n(r/s)^n + a_{n-1}(r/s)^{n-1} + ... + a_0 = 0$$
			$$ s^nf(r/s) = a_nr^n+ a_{n-1}r^{n-1}s + ... + s^na_0 = 0 $$
		Implying 
			\begin{align*}
				-a_nr^n  &= a_{n-1}r^{n-1}s + ... + s^na_0 \\
				&  = s(a_{n-1}r^{n-1} + ... + s^{n-1}a_0) 
			\end{align*}
			So $s \mid -a_n r^n$ meaning that either $s\mid a_n$ or $s
			\mid -r^n$
			because $r$ and $s$ are relatively prime the latter is
			impossible. Also note that
			\begin{align*}
				-s^na_0 & = a_nr^n+ a_{n-1}r^{n-1}s + ... + s^{n-1}ra_1\\ 
				& = r(a_nr^{n-1}+ a_{n-1}r^{n-2}s + ... +
			s^{n-1}a_1) 
			\end{align*}
			so $r \mid s^na_0$ implying $r\mid a_0$ by the same
			logic.
		\end{proof}
	\item[28]
		Let $F$ be a field and let $p(x), a_1(x),a_2(x),...,a_k(x) \in
		F[x]$, where $p(x)$ is irreducible over $F$. If $p(x) \mid
		a_1(x),a_2(x),...,a_k(x)$, show that $p(x)$ divides some
		$a(x)$.\\
		Because $p$ is irreducible we know that if $p(x) \mid a_1(x)$
		or $p(x) \mid a_2a_3...a_n$ if $p$ does not divided $a_1$ then
		$p(x) \mid a_2$ or $p(x) \mid a_3(x)a_4(x)...a_n(x)$ continuing in this
		way we can see that either $p$ divides some $a_i(x)$ along the way
		or $p$ divides $a_n(x)$.
	\item[30] If $p$ is a prime, prove that $x^{p-1} - x^{p-2} + x^{p-3}
		-...-x+1$ is irreducible over $Q$.\\
		If $f(x)$ is irreducible in a field then $f(-x)$ must also be
		irreducible in that field.
		Recall the corollary about cyclotomic polynomials, that is
		$\frac{x^p-1}{x-1}$  irreducible so
		$$\frac{(-x)^p-1}{(-x)-1} = x^{p-1} -x^{p-2}+x^{p-3}- ... - x + 1$$
		Must also be irreducible.
	\item[GAP 17.1] Factors of $x^n -1$
		\begin{align*}
			n=6 &: x-1, x+1, x^2-x+1, x^2+x+1 \\
			n=8 &: x-1, x+1, x^2+1, x^4+1 \\
			n=12 &: x-1, x+1, x^2-x+1, x^2+1, x^2+x+1, x^4-x^2+1 \\
			n=20 &:  x-1, x+1, x^2+1, x^4-x^3+x^2-x+1,
			x^4+x^3+x^2+x+1, x^8-x^6+x^4-x^2+1 \\
			n=30 &: x-1, x+1, x^2-x+1, x^2+x+1,
			x^4-x^3+x^2-x+1,x^4+x^3+x^2+x+1,\\
			&x^8-x^7+x^5-x^4+x^3-x+1,x^8+x^7-x^5-x^4-x^3+x+1
		\end{align*}
		Conjecture: All coefficients on factors of $x^n-1$ will be one
		or zero. Also the degree of any factor of $x^n-1$ is a power of
		two.
		\begin{align*}
			n=40 &: x-1, x+1, x^2-x+1, x^2+x+1, x^4-x^3+x^2-x+1,
			x^4+x^3+x^2+x+1 ...\\
			n=50 &: x-1, x+1, x^4-x^3+x^2-x+1,
			x^4+x^3+x^2+x+1,x^{20}-x^{15}+x^{10}-x^{5}+1...\\
		\end{align*}
		We can see we've found a counter example to the second part of
		our conjecture as $20$ is not a power of two.
	\item[GAP 17.2]
		\begin{enumerate}
		\item $ x^5 + 9x^4 + 12x^2 $
			This looks like an example of Eisenstein criterion but
				it's not.
				$$x^5+9x^4+12x^2 = x^2 ( x^3+9x^2+12)$$
		\item $ x^4 + x + 1$
			Is irreducible.
		\item $x^4+3x^2+1 $
			$$x^4+3x^2+1 = x^4+1 \text{ mod } 3$$
			So it is irreducible in $Q$.
		\item $ x^5+5x^2+1 $
			Is irreducible.
		\item $ 21x^3 - 3x^2+ 2x+9$
			$$ 21x^3 - 3x^2+ 2x+9 = x^3 + x^2 + 1 \text{ mod } 2$$
			So it is irreducible in $Q$.

		\end{enumerate}

\end{description}
\end{document}

